Efficient Coalition Formation \\ for Web Services

### 2013-07-11 papers/coalition-journal-extension/coalition_journal.tex
Changes

The need for highly available and responsive services has called
for grouping and collaborative mechanisms of loosely-coupled web
services, particularly in business settings. The idea of grouping
web services within communities and the way those communities are
engineered so that web services can better collaborate have been
proposed and investigated in
\cite{DBLP:journals/ijebr/MaamarSTBB09,DBLP:journals/internet/BenatallahSD03,Rosario:2008:PQS:1512146.1512290}.
Communities are virtual groups of web services having similar
functionalities \cite{Zeng:2003:QDW:775152.775211, Paik:2005:TSS:2229263.2230038,Medjahed05adynamic,Liris-3375}, but probably different non-functional quality
attributes, which form the QoS parameters. When communities are
used, users send their requests to the masters of those
communities, which are responsible of managing the communities,
forwarding the requests to the suitable member web services and
checking the credentials of those members. Communities aim to
provide higher service availability and performance than what
individual web services can provide. The high availability of
services and the community resilience to failure are guaranteed
since web services can cooperate and replace each other within the
same community and since there is no single point of failure in
the communities architecture.

>>>>

The need for highly available and responsive services has called
for grouping and collaborative mechanisms of loosely-coupled web
services, particularly in business settings. The idea of grouping
web services within communities and the way those communities are
engineered so that web services can better collaborate have been
proposed and investigated in
\cite{DBLP:journals/ijebr/MaamarSTBB09,DBLP:journals/internet/BenatallahSD03,Rosario:2008:PQS:1512146.1512290}.
Communities are virtual groups of web services having similar
functionalities \cite{Zeng:2003:QDW:775152.775211, Paik:2005:TSS:2229263.2230038,Medjahed05adynamic,10.1109/ARES.2008.7}, but probably different non-functional quality
attributes, which form the QoS parameters. When communities are
used, users send their requests to the masters of those
communities, which are responsible of managing the communities,
forwarding the requests to the suitable member web services and
checking the credentials of those members. Communities aim to
provide higher service availability and performance than what
individual web services can provide. The high availability of
services and the community resilience to failure are guaranteed
since web services can cooperate and replace each other within the
same community and since there is no single point of failure in
the communities architecture.
